---
title: "Discussion_single year (ELAPSE)"
author: "Youchen"
date: "01/26/2021"
output: html_document
  # slidy_presentation: default
  # ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.width = 6, fig.height = 6, warning=F)
source("../EXPANSE_algorithm/scr/fun_call_lib.R")
library(kableExtra)
```
```{r read data}
eu_bnd <- st_read("../expanse_shp/eu_expanse2.shp")

```

```{r read prediction results (5-fold test data)} 
# Here we read the predictions for test data from all five-folds
csv_names <- paste0('NO2_5cv_', paste0('run2_',c('08-10', '09-11', '10-12', '08-12')))
years <- list(2008:2010, 2009:2011, 2010:2012, 2008:2012)
all_test <- lapply(paste0("data/workingData/", csv_names, ".csv"), read.csv)
# lapply(all_test, nrow)
```

The predictors used in SLR, GWR, RF were the same.

```{r predictors in LUR}
source("../EXPANSE_algorithm/scr/fun_call_predictor.R")
pred_c_rf <- c(pred_c, 'year', 'zoneID') #"x_trun", "y_trun"
x_varname = names(all_test[[1]] %>% dplyr::select(matches(pred_c_rf)))
print("Predictors used:")
print(x_varname)


```



# Location

The datasets were randomly divided into training and test data, using 'type_of_st' and 'climate_zone' as stratification.


```{r fig.height=6, fig.width=10}
tmap_mode('plot')
source("../EXPANSE_algorithm/scr/fun_read_data.R")
maps_l <- lapply(seq_along(years), function(yr_i){
   no2_e_09_11 <- subset_df_yrs(no2_e_all, years[[yr_i]])
   # data_all <- no2_e_09_11
   print(paste0("year: ", unique(no2_e_09_11$year)))
   source("../EXPANSE_algorithm/scr/fun_create_fold.R")
   data_all1 <- create_fold(no2_e_09_11, seed)
   EU_sp <- st_as_sf(data_all1, coords = c("Xcoord", "Ycoord"))
   st_crs(EU_sp) <- st_crs(3035)
   
   map_1 <- tm_shape(EU_sp) +
      tm_dots(size = 0.05, col="nfold",   # col = "NO2",          # popup.vars for showing values
              title = paste0('nfold in year ', unique(no2_e_09_11$year)), palette=viridis(5), style = "cat"  #,  palette=viridis(5), style=="fixed"
      )+
      tm_shape(eu_bnd)+
      tm_borders()
   map_1
})
do.call(tmap_arrange, maps_l)
```

# Five-fold cross-validation


```{r}


show_EM <- function(all_df_i){
   # gwr=all_test[[all_df_i]]$gwr
   slr=all_test[[all_df_i]]$slr
   rf=all_test[[all_df_i]]$rf
   df_all <- data.frame(slr=error_matrix(all_test[[all_df_i]]$obs, slr),
           # gwr=error_matrix(all_test[[all_df_i]]$obs, gwr),
           rf=error_matrix(all_test[[all_df_i]]$obs, rf),
           yr=csv_names[[all_df_i]])[c(1,5,7),]
   df_all$EM = row.names(df_all)
   df_all
}
em_df <- lapply(seq_along(all_test), show_EM)
em_df <- do.call(rbind, em_df)
ggplot(em_df %>% filter(EM=='rsq') %>%  gather("model", "values", -c("yr", "EM")), aes(x=yr, y=values, fill=model))+
      geom_bar(stat="identity", position = "dodge2")+
      # facet_grid(EM~., scales ='free')+
      # labs(title=years[[i]])+
      theme(axis.title = element_text(size = 18),
          axis.text = element_text(size = 16),
          legend.title = element_text(size = 16),
          legend.text = element_text(size = 16),
          strip.text.y = element_text(size = 15))

# ggplot(perfm)+
#       geom_boxplot(aes(x=model, y=rsq))+
#       facet_grid(df_type~., scales ='free')+
#       labs(title=years[[i]])+
#       theme(axis.title = element_text(size = 18),
#           axis.text = element_text(size = 16),
#           legend.title = element_text(size = 16),
#           legend.text = element_text(size = 16))


```

The longer the time periods, the more important the year is in random forests.


```{r selected predictors in slr, fig.width = 8, fig.height = 3.6}
files <- list.files("data/workingData/", "SLR_summary_model_run2_")[grepl("fold", list.files("data/workingData/", "SLR_summary_model_run2_"))]
comp_rf_slr <- function(csv_i){
   slr_name <- files[csv_i]
   yr <- strsplit(slr_name, "_")[[1]][5]
   nfold <- (strsplit(slr_name, "_")[[1]][7] %>% strsplit(., ".csv"))[[1]] %>% as.numeric()
   # rf_name <- paste0("RF_vi_o_", yr, "_fold_", nfold, ".csv")
   slr_result <- read.csv(paste0("data/workingData/", slr_name), header=T)
   slr_result$yr <- yr
   slr_result$nfold <- nfold
   slr_result$increR2[1]=0
   slr_result$incredR2 <- c(0, diff(slr_result$increR2))
   p1 <- ggplot(slr_result)+
      geom_col(aes(x=reorder(variables, incredR2), y=incredR2), 
               position = "dodge2", fill='khaki')+
      coord_flip() +
      theme_light()+
      labs(x = 'variable', y = 'increased R2',
           title = paste0(yr, "_fold_", nfold))+
      # facet_grid(EM~., scales ='free')+
      # labs(title=years[[i]])+
      theme(axis.title = element_text(size = 18),
            axis.text = element_text(size = 16),
            legend.title = element_text(size = 16),
            legend.text = element_text(size = 16),
            strip.text.y = element_text(size = 15))
   # rf_vi <- read.csv(paste0("data/workingData/", rf_name))
   source("../EXPANSE_algorithm/scr/fun_plot_rf_vi.R")
   p2 <- plot_rf_vi(paste0("run2_", yr, "_fold_", nfold), var_no = 20)
   grid.arrange(p1, p2, nrow=1)
}

# comp_rf_slr(4)
lapply(seq_along(files), comp_rf_slr)
```


# Performance matrix

* Supervised Linear regression (SLR)
* Geographically weighted regression (GWR)
* Random forests (RF)

Training data was used for training the models using these three algorithms. Then the test data was used for evaluating model performance.

Averaged error matrix from all folds:

```{r, echo=F}
perfm <- lapply(paste0("data/workingData/", list.files("data/workingData/", paste0("perf_m_run2_"))), read.csv)
perfm <- do.call(rbind, perfm)
perfmm <- perfm %>% filter(df_type=="test") %>% mutate(run=substr(csv_name, 1, 10), 
                            nfold=substr(csv_name, 12, 17))
ggplot(perfmm, aes(x=run, y=rsq, fill=nfold, group=nfold))+
    geom_bar(stat="identity", position = "dodge2")+
      facet_grid(model~., scales ='free')+
      # labs(title=years[[i]])+
      theme(axis.title = element_text(size = 18),
          axis.text = element_text(size = 16),
          legend.title = element_text(size = 16),
          legend.text = element_text(size = 16),
          strip.text.y = element_text(size = 15))
```



